Crowd density estimation from Wi-Fi positioning data in the Amsterdam Arena

### 2016-06-28 PaperOnSmoothing/draft-31052016.tex
pictures improved

The rest of the paper is organized as follows.....*******

@@

Sonja:Mention somewhere that in the documentary of the LP disaster people were raising their phones up to look for a way out. (which is good , less blockage of signals)
\subsection{Issues with positioning (title to reconsider)}

Under ideal circumstances, the positioning itself would suffice to estimate the crowd density per region of interest:  every few seconds we would only need to count the number of estimates that fall in the region of interest. However, we have observed several issues, which are not related to the mathematical methodology behind the positioning step, that prevent us to apply direct counting. 
\begin{enumerate}
	\item
	{\it Bimodal distributions of coordinates estimations}. We have sampled randomly 20 MAC addresses and plotted the estimations of their coordinates through time, where we have plotted only the estimations with a relatively small uncertainty. We observed persistent bimodal distribution of the estimations, an example of which can be seen in Fig. \ref{fig:bimodal}. 
		\begin{figure}[h!]
			\centering
			\includegraphics[width=100mm]{bimodal.jpg}
			\caption{Trilateration can lead to multiple local optima (cut the lower part from the picture)}
			\label{fig:bimodal}
		\end{figure} 
	This figure shows the estimated x-coordinates through time of a static, 24 hours persistent MAC address. Because we did not observe  bi-modal distributions in the signal strengths, the bi-modal distribution of the positions estimates can be explained by the multiple local optima situation. Namely, due to signal interference, when the optimization of the estimation of location of a certain MAC address is performed, there can be multiple local optima that are equally good candidates. For example, consider Fig. \ref{fig:trilateration_problem} \footnote{Picture courtesy of http://math.stackexchange.com/questions/42537/trilateration-with-bounds}. In the center of every ring there is a Wi-Fi router, that has estimated signal strength to a certain MAC device with a certain error range. The error range is represented by the thickness of the ring. Then, there are two possible regions which are equally good candidates for the positioning of the MAC device, and those regions are the two darkest regions where all three rings overlap. Note that the problem can arise regardless of the thickness of the rings or the number of Wi-Fi routers. 	
	\begin{figure}[h!]
		\centering
		\includegraphics[width=40mm]{trilateration_problem.jpg}
		\caption{Trilateration can lead to multiple local optima}
		\label{fig:trilateration_problem}
	\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=130mm]{RatioRandNonrand.jpeg}
	\caption{Estimations of x-coordinates of a static MAC device as a function of time}
	\label{fig:randomized}
\end{figure}

@@

>>>>

The rest of the paper is organized as follows.....

@@

\subsection{Issues with positioning (title to reconsider)}

Under ideal circumstances, the positioning itself would suffice to estimate the crowd density per region of interest:  every few seconds we would only need to count the number of estimates that fall in the region of interest. However, we have observed several issues, which are not related to the mathematical methodology behind the positioning step, that prevent us to apply direct counting. 
\begin{enumerate}
	\item
	{\it Bimodal distributions of coordinates estimations}. We have sampled randomly 20 MAC addresses and plotted the estimations of their coordinates through time, where we have plotted only the estimations with a relatively small uncertainty. We observed persistent bimodal distribution of the estimations, an example of which can be seen in Fig. \ref{fig:bimodal}. 
		\begin{figure}[h!]
			\centering
			\includegraphics[width=120mm]{bimodal.jpg}
			\caption{Estimation of x-coordinate of a static MAC device through time with error}
			\label{fig:bimodal}
		\end{figure} 
	This figure shows the estimated x-coordinates through time of a static, 24 hours persistent MAC address. Because we did not observe  bi-modal distributions in the signal strengths, the bi-modal distribution of the positions estimates can be explained by the multiple local optima situation. Namely, due to signal interference, when the optimization of the estimation of location of a certain MAC address is performed, there can be multiple local optima that are equally good candidates. For example, consider Fig. \ref{fig:trilateration_problem} \footnote{Picture courtesy of http://math.stackexchange.com/questions/42537/trilateration-with-bounds}. In the center of every ring there is a Wi-Fi router, that has estimated signal strength to a certain MAC device with a certain error range. The error range is represented by the thickness of the ring. Then, there are two possible regions which are equally good candidates for the positioning of the MAC device, and those regions are the two darkest regions where all three rings overlap. Note that the problem can arise regardless of the thickness of the rings or the number of Wi-Fi routers. 	
	\begin{figure}[h!]
		\centering
		\includegraphics[width=40mm]{trilateration_problem.jpg}
		\caption{Trilateration can lead to multiple local optima}
		\label{fig:trilateration_problem}
	\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=130mm]{RatioRandNonrand.jpeg}
	\caption{Ratio between randomized and non-randomized addresses observed per minute}
	\label{fig:randomized}
\end{figure}

@@

Sonja:Mention somewhere that in the documentary of the LP disaster people were raising their phones up to look for a way out. (which is good , less blockage of signals)
